Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants\thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN 712689 SC$^2$.}

### 2017-05-04 cav2017/cav2017.tex
order

We give the results in Table~\ref{tab:results}.  Here \textit{Benchmark} is
the name of the respective benchmark, \textit{order} is the number of states, 
$\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used to model the plant, while
\textit{Time} is the total time required to synthesize a \blue{stable} controller
for the given plant, for CEGIS with multi-staged verification as well as
abstraction-based CEGIS.  Timeouts are indicated by~\xmark.  The precision
for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is chosen to be
$I_c = 8$, $F_c = 8$.

>>>>

We give the results in Table~\ref{tab:results}.  Here \textit{Benchmark} is
the name of the respective benchmark, \textit{order} is the number of
continuous variables, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the
fixed-point precision used to model the plant, while \textit{Time} is the
total time required to synthesize a \blue{stable} controller for the given
plant with the given method.  Timeouts are indicated by~\xmark.  The
precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
chosen to be $I_c = 8$, $F_c = 8$.
